\documentclass[11pt,letterpaper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{orange}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.85]{geometry}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\name{Bert JW}{Regeer}
%\title{CV}                               % optional, remove / comment the line if not wanted
\address{Parker, CO 80138}{}{}% optional, remove / comment the line if not wanted; the "postcode city" and "country" arguments can be omitted or provided empty
\phone[mobile]{+1~480~264~0039}                   % optional, remove / comment the line if not wanted; the optional "type" of the phone can be "mobile" (default), "fixed" or "fax"
\email{bertjw@regeer.org}                               % optional, remove / comment the line if not wanted
\homepage{bertjwregeer.com}                         % optional, remove / comment the line if not wanted
\social[linkedin]{bertjwregeer}                        % optional, remove / comment the line if not wanted
\social[twitter]{bertjwregeer}                             % optional, remove / comment the line if not wanted
\social[github]{bertjwregeer}                              % optional, remove / comment the line if not wanted
%\extrainfo{additional information}                 % optional, remove / comment the line if not wanted
%\photo[64pt][0.4pt]{picture}                       % optional, remove / comment the line if not wanted; '64pt' is the height the picture must be resized to, 0.4pt is the thickness of the frame around it (put it to 0pt for no frame) and 'picture' is the name of the picture file
%\quote{Some quote}                                 % optional, remove / comment the line if not wanted


%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%\begin{CJK*}{UTF8}{gbsn}                          % to typeset your resume in Chinese using CJK
%-----       resume       ---------------------------------------------------------
\makecvtitle

\section{Profile}
Bert is an highly motivated individual, someone who enjoys exploring new technologies and applying his gained knowledge in new and exciting ways. His strongest point are his knowledge of the UNIX/Linux system environment with an intimate knowledge and understanding. FreeBSD is Bert's operating system of choice, with extensive knowledge of administration and deployment on top of FreeBSD. While C++ and Python are currently the two primary programming languages, almost any new language, technology, or idea can be easily learned and adapted within a relatively short period of time. Working with customers to solve the challenges and exploiting his knowledge to assist his clients, Bert is able to work with others to form unique and innovative solutions to the most difficult challenges. Bert has a variety of interests outside of software and system administration including hardware development (PCB's, microcontrollers, LED's), and cooking.

\section{Skills}
\cvitem{Languages}{C++ (including 11+), C (including 11+), Python (2.x and 3.x), Java, C\#, JavaScript}
\cvitem{Databases}{PostgreSQL, MySQL, and SQLite 3}
\cvitem{Versioning}{git, Mercurial, Subversion and CVS}
\cvitem{Security}{Cryptography primitives and fundamentals, including understanding and mitigating common pitfalls. Building secure software, and the ability to understand and effectively address various security issues}
\cvitem{Other}{Bugtraq, JIRA, Confluence, OpenFire (Jabber), Gitlab, Gitorious, Sphinx (Documentation), \LaTeX , Doxygen, Klocwork, 
VMWare (Fusion, Workstation), VirtualBox, KVM, Jenkins, postfix, nginx, uwsgi, varnish}
\cvitem{}{IPv4 and IPv6 deployment and software compatibility.}
\cvitem{OS}{FreeBSD (jails), Mac OS X (10.3 - 10.9), OpenIndiana (Solaris) (zones), Linux (Ubuntu, CentOS), Windows (XP, Vista, 7, 8), VMWare ESXi}


\section{Experience}
\subsection{Professional}
\cventry{2012--current}{Owner, founder and officer}{Tumble Inc}{Parker, CO}{}{Owner and founder of a two man company that builds custom software.\newline{}Worked together with my partner on customer acquisition and development.
\begin{itemize}
\item Manage the companies IT infrastructure
\item Prepare quotes for proposals
\item Work with potential clients on figuring out their needs and how to best build what they require
\item Distil requests down to action points that can be delivered on within a certain time line
\end{itemize}}

\cventry{2010--current}{Server Systems Integrator}{Absio Corporation}{Littleton, CO}{}{Team lead and programmer that built large scalable, fault tolerant and high availability systems that can scale both vertically and horizontally.
\begin{itemize}
\item Lead of small team (40\% of time working as team lead, 60\% time spent developing software)
\item Drafted, implemented, and led the various teams on all cryptographic decisions for the product
\item Successful deployment to production for Absio's commercial launch
\item Helped architect, designed, and built C++ and Python projects to support the business requirements
\item Worked with stakeholders to develop and work on future project plans and ideas
\item Built various small one-off websites as required to complete various project goals
\item Other tasks included:
	\begin{itemize}
	\item Manage OpenIndiana (zones), FreeBSD (jails), and Linux
	\item Built and set-up OpenStack on Linux to allow developers to easily spin up VM's
	\item Managed/setup internal git repository hosting using Gitlab (previous Gitorious)
	\item Managed/setup internal Jabber server (OpenFire) to allow for easy communication between developers
	\item Managed/setup internal Jenkins continuous integration server to allow for builds upon push to git
	\end{itemize}
\end{itemize}
Absio was a small startup when I joined and I had the opportunity to wear a lot of different "hats", in the process learning about various aspects of the business and most importantly various parts of server side development.
}

\cventry{2002--current}{System Administrator}{osnn.net}{}{}{Administer hosting for a variety of online websites using Apache, PHP, and qmail on FreeBSD. Migrated with zero downtime the websites from one location to another.
\begin{itemize}
\item Manage various services such as Apache, Lighttpd and qmail
\item Monitor services for attempted intrusions and outdated software, and update as required
\end{itemize}}

\subsection{Contract \& Short Term}
\cventry{2006--2013}{System Administrator}{Partners in Print}{}{}{Provided on-call support for FreeBSD based web hosting. Assisted business operations by maintaining Apache, PHP, qmail, and DNS (tinydns). Planned and executed a move of the customers hosting from a US based host to a UK based host.
\begin{itemize}
\item Managed various services such as Apache, PHP and qmail
\item Tuned server resources and monitor server for intrusions
\item Built and managed custom backup solution that allowed the business to recover in the case of failed hardware or accidental deletions of content
\end{itemize}}

\cventry{2007}{Security Audit}{University of Advancing Technology}{Tempe, AZ}{}{With a small team of colleagues assessed the security of the various web properties students could access. Pentested internal systems against possible insider security threats and provided a report on potential vulnerabilities.
\begin{itemize}
\item General network security audit
\item Enumerated exploits on the internal student intranet websites
\item Identified and documented flaws in running services on the computers on campus
\item Analyzed and assessed the security of proprietary network protocols for various services
\item Responsibly disclosed various data leaks and security holes to the client
\end{itemize}
}

\subsection{Internship}
\cventry{2009}{Website developer}{AEC Consultants}{Phoenix, AZ}{}{Built a brand new web presence for AEC Consultants using PHP and the Zend Framework. Templated and designed the new website under guidance of the CEO to fit his vision of what the company should have available.
\begin{itemize}
\item Built and designed a complete site using best practices in PHP (with Zend Framework)
\item Designed and built MySQL database tables to store the data required (portfolio/existing projects and new request for proposals)
\item Copy edited and designed the layout of various static pages (contact/about us/services)
\end{itemize}}

\subsection{Volunteer}
\cventry{2011--current}{Goon}{DEF CON}{Las Vegas}{}{Gooning in the contest area, the largest part of the conference, within DEF CON primarily involves managing and working with various other CnE goons, hotel staff, and event staff to make sure the various contest and event organisers have the resources required. Built and maintain the DEF CON Contest and Event website where organisers can register their contests/events and where people can come find information regarding the same.}

\cventry{2008--2010}{Volunteer Worker}{Blackhat}{Las Vegas}{}{Participated in a large 40+ volunteer effort to organize and run the Black Hat Las Vegas conference which included laying down network and power cables, setting up classrooms, directing attendees around the conference and registering them.}

\section{Interests \& Projects}
\cvitem{funcptr}{Bert maintains a technical notebook named funcptr (short for function pointer) at http://funcptr.net/. It is there that he posts various technical tips and tricks as well as engineering challenges he has solved. It has been steadily growing in traffic, and has helped many people with similar problems.}
\cvitem{open source}{Free and available source code is a boon to any developer that is continually learning. Bert himself is a staunch supporter of open source and has released various projects under an open source license. At the moment he has been working extensively with the Pylons web framework team on improving Pyramid a Python web framework. Bert has also continued working on various personal projects, with on-going code commits and pushes to Github.}
\cvitem{near space}{In the past, Bert worked with a team of other students at the University of Advancing Technology to design, and build a near space balloon capsule that was able to take pictures at a defined interval, take atmospheric measurements, and return it's location data using APRS over HAM radio. The team had two successful launches, named CONNERY-1 and CONNERY-2 respectively, with absolutely amazing pictures from the two flights.}

\section{Education}
\cventry{2006--2009}{Software Engineering}{University of Advancing Technology}{Tempe, AZ}{}{Bachelor of Science: Software Engineering \newline{Major: Computer Programming}}

\clearpage
\end{document}


%% end of file `template.tex'.
